%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring
% the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%------------------------------------------------------------------------------

\documentclass[8pt]{resume} % Use the custom resume.cls style

% Document margins
\usepackage[left=0.5in,top=0.35in,right=0.5in,bottom=0.35in]{geometry}
\usepackage{multicol}
\usepackage{hyperref}

\name{Mubeen Shaik} % Your name

\begin{document}
\begin{flushright}
Phone: +918106220567\\
Email: mubeena6sk@gmail.com\\
Github: www.github.com/Mubeena6sk
\end{flushright}

%------------------------------------------------------------------------------
%	EDUCATION SECTION
%------------------------------------------------------------------------------
\begin{rSection}{Education}

{\bf Rajiv Gandhi University of Knowledge Technologies, Basar} \hfill {\em Estimated May 2021} \\ 
B.Tech in Computer Science \hfill Overall CGPA: 8.1

{\bf Rajiv Gandhi University of Knowledge Technologies, Basar} \hfill {\em May 2017} \\ 
Pre-University Course in MPC \hfill Overall CGPA: 8.3
\end{rSection}

%------------------------------------------------------------------------------
%   SKILLS (technical expertise?)
%------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}

    \begin{multicols}{2}[]
{\bf Languages:} Python, JavaScript, C, Java, \LaTeX \\
{\bf Platforms:} Linux, Android, Windows\\
{\bf Databases:} PHPMyadmin, MySQL,Oracle\\
{\bf Fundamentals:} Data Structures and Algorithms, OOPs\\
{\bf Virtualization/Cloud:} GCP, IBM Cloud\\
{\bf Tools/Softwares:} Git, Github, Anaconda, Eclipse\\
{\bf Web Technologies:} HTML,CSS, PHP, JSP\\
{\bf Frameworks:} Flask, Tensorflow, Flutter
    \end{multicols}
\end{rSection}

%------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%------------------------------------------------------------------------------

\begin{rSection}{Internship Experience}

    \begin{rSubsection}
        {IIIT Hyderabad}
        {\em June 2020 - August 2020}
        {Research Intern   \scriptsize \url{https://github.com/Mubeena6sk/proctor_system }} 
      {Hyderabad}
    \item Led a research project "\emph{Remote Proctoring system for online exams}" , implementing object detection algorithms(YOLO \& OpenCV) that are trained on {\bf 5-celebrity faces }dataset. 
    \item {\bf Added two additional features}; multiple persons detection and user authentication during exam to the existing paper "\emph{Automated Online Exam Proctoring} by Yoused Atoum. 
    \item Implemented and Integrated the deep learning models with front-end using Flask and XAMPP database which successfully passed all validation tests.
    \end{rSubsection}

%------------------------------------------------------------------------------

    \begin{rSubsection}
        {LifeOfGirl}
        {\em March 2020 - June 2020}
        {Application Developer Intern}
        {Hyderabad}
    \item  Tested , Reviewed the LOG application. Worked on improving the code applying the principles of Object oriented programming.
    \item Implemented GUI elements and data structures to {\bf create a new feature called Gyroscope} adding t-SNE Machine learning algorithm to keep track of acceleration.
    \end{rSubsection}
%

\end{rSection}
%------------------------------------------------------------------------------
%   Start two-column section
%------------------------------------------------------------------------------

%------------------------------------------------------------------------------
%   Projects
%------------------------------------------------------------------------------

 \begin{rSection}{Selected Projects}
    {\bf Khushi Admin Application } -\emph{\bf Freelancing Project} {\scriptsize \url{https://gitlab.com/app_viral_khushi/khushi_android_admin_app}} \hfill{\em May,2020}
    \begin{list}{$\bullet$}{\leftmargin=1em}
    \itemsep -0.5em \vspace{-0.5em}
        \item An cloud-based Android application built on FFMPEG library that takes video inputs and does necessary tweakings such as watermarks, resizing, trims and other mp4 and mp3 effects.The resultant video is pushed onto amazon bucket for streaming.
    \end{list}

%------------------------------------------------------------------------------

    {\bf Women Safety App} - (Java, Speech Recognition) {\scriptsize \url{https://github.com/Mubeena6sk/swarasthr}} \hfill {\em Jan,2020}
    \begin{list}{$\bullet$}{\leftmargin=1em}
    \itemsep -0.5em \vspace{-0.5em}
        \item  Developed and designed the app that trained over {\bf 1000 sound events}(scream and non-scream) using {\bf SVM classifer} that produces a scream alert. Worked with Location class deriving latitude and longitude and Telecom package for making phone calls and sms services without human intervention.
    \end{list}

%------------------------------------------------------------------------------

    {\bf Android Syllabus LookUp App} - (Flutter, Android Studio, Dart){\scriptsize \url{ https://github.com/Mubeena6sk/Syllabusapp_flutter}} \hfill {\em Aug,2019}
    \begin{list}{$\bullet$}{\leftmargin=1em}
    \itemsep -0.5em \vspace{-0.5em}
        \item An Android UI application that helps to get the syllabus of a particular branch-year-sem
 provided by the user. All that the user needs to do is select his preferences and the syllabus will be automatically shown. 
    \end{list}
\end{rSection}


%------------------------------------------------------------------------------
%   Activities	
%------------------------------------------------------------------------------

\begin{rSection}{Activities and Achievements}

    {\bf SoundOfAI - OpenSource Research Community}: Contributor, {\em 2020-Present}

%------------------------------------------------------------------------------

    {\bf  Student Innovation Award}: {\bf WES} Hyderabad, {\em 2020} for Women Safety App

%------------------------------------------------------------------------------
{\bf  Programming in Java}: Certified with 96\% conducted by NPTEL online certification and been in the {\bf Top-5\%} among the students who participated in 2019.
%------------------------------------------------------------------------------

%------------------------------------------------------------------------------

\end{rSection}


\end{document}
